The Proofs

### 2023-10-17 proofs/tex/subst-algo-lemmas.tex
wip

  This way, by \cref{lemma:subst-eq-algovar}, 
  $[[Θ ⊢ [uσ1]uP ≈ [uσ2]uP]]$ implies 
  $[[nf(uσ1)|(uv nf(uP)) = nf(uσ2)|(uv nf(uP))]]$.
  Then by \cref{lemma:uv-nf}, 
  $[[nf(uσ1)|(uv uP) = nf(uσ2)|(uv uP)]]$,
  and by ${{corollary:subst-subt-equiv-algorithmization}}$,
  $[[Θ ⊢ uσ1 ≈ uσ2 : uv uP]]$.

>>>>

  This way, by \cref{lemma:subst-eq-algovar}, 
  $[[Θ ⊢ [uσ1]uP ≈ [uσ2]uP]]$ implies 
  $[[nf(uσ1)|(uv nf(uP)) = nf(uσ2)|(uv nf(uP))]]$.
  Then by \cref{lemma:uv-nf}, 
  $[[nf(uσ1)|(uv uP) = nf(uσ2)|(uv uP)]]$,
  and by \cref{corollary:subst-subt-equiv-algorithmization},
  $[[Θ ⊢ uσ1 ≈ uσ2 : uv uP]]$.
